---
title: "204_hw2"
author: "Katherine Rosencrance"
date: "4/21/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# attach packages
library(here)
library(tidyverse)

```

# #1. Plot marginal abatement cost data for each irrigation district
```{r}
#Read in the data
water_districts <- read_csv(here("Water_Districts.csv"))

# plot data from each district
district_plot <- ggplot(data = water_districts, aes(x= Reduction)) + 
  geom_smooth(method = "lm", aes(y = MC_Kern), color = "darkred") + 
  geom_smooth(method = "lm", aes(y = MC_Mojave), color="steelblue")+
  geom_smooth(method = "lm", aes(y = MC_Antelope), color = "green")+
  geom_smooth(method = "lm", aes(y = MC_Ventura), color = "yellow")+
  labs(x = "Reduction in AF", y = "Price ($/AF) ")+
  theme_classic()
district_plot

```

```{r}
# plot data for each district separately
MC_kern <- ggplot(data = water_districts, aes(x = Reduction, y = MC_Kern))+
  geom_point()
MC_kern

MC_mojave <- ggplot(data = water_districts, aes(x = Reduction, y = MC_Mojave))+
  geom_point()
MC_mojave

MC_antelope <- ggplot(data = water_districts, aes(x = Reduction, y = MC_Antelope))+
  geom_point()
MC_antelope

MC_ventura <- ggplot(data = water_districts, aes(x = Reduction, y = MC_Ventura))+
  geom_point()
MC_ventura
```

```{r}
# linear models for each district
model_kern <- lm(MC_Kern ~ 0 + Reduction, data= water_districts)
B = model_kern$coefficient[1]
predicted_mc_kern <- B*seq(0, 150, 500)

model_mojave <- lm(MC_Mojave ~ 0 + Reduction, data= water_districts)
B = model_mojave$coefficient[1]
predicted_mc_mojave <- B*seq(0, 150, 500)

model_antelope <- lm(MC_Antelope ~ 0 + Reduction, data= water_districts)
B = model_antelope$coefficient[1]
predicted_mc_antelope <- B*seq(0, 150, 500)

model_ventura <- lm(MC_Ventura ~ 0 + Reduction, data= water_districts)
B = model_ventura$coefficient[1]
predicted_mc_ventura <- B*seq(0, 150, 500)

summary(model_kern)
summary(model_antelope)
summary(model_mojave)
summary(model_ventura)

# store slopes
kern_slope <- model_kern$coefficient[1]
mojave_slope <- model_mojave$coefficient[1]
antelope_slope <- model_antelope$coefficient[1]
ventura_slope <- model_ventura$coefficient[1]
```

# #2.Derive each districts demand curve for water

```{r}
#Baselines
kern_baseline <- 150
mojave_baseline <- 140 
antelope_baseline <- 220
ventura_baseline <- 245

# Demand/use equations stored as functions
kern_mb <- function(x){kern_slope*(kern_baseline-x)}
mojave_mb <- function(x){mojave_slope*(mojave_baseline-x)}
antelope_mb <- function(x){antelope_slope*(antelope_baseline-x)}
ventura_mb <- function(x){ventura_slope*(ventura_baseline-x)}

# Plot demand curves
ggplot(data.frame(x = c(0,250)), aes(x = x)) +
  stat_function(fun = kern_mb, color = "darkred")+
  stat_function(fun = mojave_mb, color = "steelblue")+
  stat_function(fun = antelope_mb, color = "green")+
  stat_function(fun = ventura_mb, color = "yellow")+
  theme_minimal()+
  ylim(0, 750) +
  labs(x = "Water used (AF)", y = "Price ($/AF)", title = "Demand for Water")
```
# #3 (1) calculate the stringency of the policy (defined below for each intervention) required to achieve the 500 AF target, (2) calculate the total cost of meeting the target using that approach, (3) calculate the cost to each district, and (4) calculate the tax revenue generated

## Cap without trade
```{r}
# stringency of policy = 255/755 or 0.338

# Total cost of meeting target

# P* using the new Q* 
kern_p <- {kern_slope*(kern_baseline-99.3)}
mojave_p <- {mojave_slope*(mojave_baseline-92.68)}
antelope_p <- {antelope_slope*(antelope_baseline-145.64)}
ventura_p <- {ventura_slope*(ventura_baseline-162.19)}

kern_p
mojave_p
antelope_p
ventura_p

# calculate area of triangle using 1/2(P*)(change in Q) to get individual costs
kern_cost <- 0.5*(kern_p)*(50.7)
mojave_cost <- 0.5*(mojave_p)*(47.32)
antelope_cost <- 0.5*(antelope_p)*(74.36)
ventura_cost <- 0.5*(ventura_p)*(82.81)

# total cost by adding up all district costs
total_cost <- kern_cost +
mojave_cost +
antelope_cost +
ventura_cost

total_cost

```

## Tax on water use
```{r}
# stringency calculated by horizontally summing the 4 MC(A) curves
horizontal_sum <- (1/kern_slope)+(1/mojave_slope)+(1/antelope_slope)+(1/ventura_slope)
tau_star <- 255/horizontal_sum
tau_star

#calculate total cost by getting area of triangle from aggregate MC curve
total_cost <- 0.5*tau_star*255
total_cost

#calculate individual cost for each district

#determine abatement for each district
kern_abate <- (1/kern_slope)*tau_star
mojave_abate <- (1/mojave_slope)*tau_star
antelope_abate <- (1/antelope_slope)*tau_star
ventura_abate <- (1/ventura_slope)*tau_star

kern_abate
mojave_abate
antelope_abate
ventura_abate

#determine area of triangle using abatement and tax (tau_star)
kern_cost_tax <- 0.5*(kern_abate*tau_star)
mojave_cost_tax <- 0.5*(mojave_abate*tau_star)
antelope_cost_tax <- 0.5*(antelope_abate*tau_star)
ventura_cost_tax <- 0.5*(ventura_abate*tau_star)

kern_cost_tax
mojave_cost_tax
antelope_cost_tax
ventura_cost_tax

# determine tax revenue by multiplying tax by abatement
government_revenue <- tau_star*255
government_revenue

```
## Cap and trade
```{r}
# calculate stringency of policy= abatement/baseline
kern_trade_abatement <- tau_star/kern_slope
kern_stringency <- (kern_trade_abatement)/(kern_baseline)

mojave_trade_abatement <- tau_star/mojave_slope
mojave_stringency <- (mojave_trade_abatement)/(mojave_baseline)

antelope_trade_abatement <- tau_star/antelope_slope
antelope_stringency <- (antelope_trade_abatement)/(antelope_baseline)

ventura_trade_abatement <- tau_star/ventura_slope
ventura_stringency <- (ventura_trade_abatement)/(ventura_baseline)

kern_stringency
mojave_stringency
antelope_stringency
ventura_stringency

# total cost of meeting approach
#calculate total cost by getting area of triangle from aggregate MC curve
total_cost <- 0.5*tau_star*255
total_cost

# total cost to each district
kern_post_trade_cost <- (0.5*kern_abate*tau_star)
kern_post_trade_cost
mojave_post_trade_cost <- 0.5*mojave_abate*tau_star
mojave_post_trade_cost
antelope_post_trade_cost <- 0.5*antelope_abate*tau_star
antelope_post_trade_cost
ventura_post_trade_cost <- 0.5*ventura_abate*tau_star
ventura_post_trade_cost

#Take into account cost of AF sold or bought based on the difference in abatement before and after trading
kern_trade_money <- (kern_trade_abatement-50.7)*(tau_star)
kern_trade_money
#Kern abated more than with the 1/3, so subtract amount made from selling from total cost
kern_trade_cost <- kern_post_trade_cost-kern_trade_money
kern_trade_cost

mojave_trade_money <- (mojave_trade_abatement - 47.32)*(tau_star)
mojave_trade_money
#Mojave abated less than with the 1/3, so add amount spent from buying extra to total cost 
mojave_trade_cost <- mojave_post_trade_cost-mojave_trade_money
mojave_trade_cost

antelope_trade_money <- (antelope_trade_abatement - 74.36)*tau_star
antelope_trade_money
#Antelope abated less than with the 1/3, so add amount spent from buying extra to total cost
antelope_trade_cost <- antelope_post_trade_cost-antelope_trade_money
antelope_trade_cost

ventura_trade_money <- (ventura_trade_abatement - 82.81)*tau_star
ventura_trade_money
#Ventura abated more than with the 1/3, so subtract amount made from selling from total cost
ventura_trade_cost <- ventura_post_trade_cost - ventura_trade_money
ventura_trade_cost

```

#A severe drought hits California, and it is necessary to reduce water use from 500 AF down to 300 AF. Your job is to estimate the cost of the drought (i.e., the cost of reducing water use from 500 AF to 300 AF) to each irrigation district under each policy. Considering the entire jump from status quo (755 AF) to the drought (300 AF), which policy is preferred by each irrigation district? How does your answer depend on how rights are allocated to each district (in policies (a) and (c))2?

## Cap without trade-drought
```{r}
# stringency = 200/500 = 0.4
# baseline*0.4 = new use
# P* using the new Q*
kern_p_drought <- {kern_slope*(kern_baseline-60)}
mojave_p_drought <- {mojave_slope*(mojave_baseline-56)}
antelope_p_drought <- {antelope_slope*(antelope_baseline-88)}
ventura_p_drought <- {ventura_slope*(ventura_baseline-98)}

kern_p_drought
mojave_p_drought
antelope_p_drought
ventura_p_drought

# calculate area of triangle using 1/2(P*)(change in Q) to get individual costs
kern_cost_drought <- 0.5*(kern_p_drought)*(90)
mojave_cost_drought <- 0.5*(mojave_p_drought)*(84)
antelope_cost_drought <- 0.5*(antelope_p_drought)*(132)
ventura_cost_drought <- 0.5*(ventura_p_drought)*(147)

kern_cost_drought
mojave_cost_drought
antelope_cost_drought
ventura_cost_drought
```
# Tax on water use-drought
```{r}
# stringency calculated by horizontally summing the 4 MC(A) curves
horizontal_sum <- (1/kern_slope)+(1/mojave_slope)+(1/antelope_slope)+(1/ventura_slope)
tau_star_drought <- 455/horizontal_sum
tau_star_drought

#calculate individual cost for each district

#determine abatement for each district
kern_abate_drought <- (1/kern_slope)*tau_star_drought
mojave_abate_drought <- (1/mojave_slope)*tau_star_drought
antelope_abate_drought <- (1/antelope_slope)*tau_star_drought
ventura_abate_drought <- (1/ventura_slope)*tau_star_drought

kern_abate_drought
mojave_abate_drought
antelope_abate_drought
ventura_abate_drought

#determine area of triangle using abatement and tax (tau_star_drought)
kern_cost_tax_drought <- 0.5*(kern_abate_drought*tau_star_drought)
mojave_cost_tax_drought <- 0.5*(mojave_abate_drought*tau_star_drought)
antelope_cost_tax_drought <- 0.5*(antelope_abate_drought*tau_star_drought)
ventura_cost_tax_drought <- 0.5*(ventura_abate_drought*tau_star_drought)

kern_cost_tax_drought
mojave_cost_tax_drought
antelope_cost_tax_drought
ventura_cost_tax_drought
```
# Cap and Trade-drought
```{r}
# calculate stringency of policy= baseline-abatement/abatement
kern_trade_abatement_d <- tau_star_drought/kern_slope
kern_stringency_d <- (kern_trade_abatement_d)/(kern_baseline)

mojave_trade_abatement_d <- tau_star_drought/mojave_slope
mojave_stringency_d <- (mojave_trade_abatement_d)/(mojave_baseline)

antelope_trade_abatement_d <- tau_star_drought/antelope_slope
antelope_stringency_d <- (antelope_trade_abatement_d)/(antelope_baseline)

ventura_trade_abatement_d <- tau_star_drought/ventura_slope
ventura_stringency_d <- (ventura_trade_abatement_d)/(ventura_baseline)

kern_stringency_d
mojave_stringency_d
antelope_stringency_d
ventura_stringency_d

# total cost to each district
kern_post_trade_cost_d <- (0.5*kern_abate_drought*tau_star_drought)
kern_post_trade_cost_d
mojave_post_trade_cost_d <- 0.5*mojave_abate_drought*tau_star_drought
mojave_post_trade_cost_d
antelope_post_trade_cost_d <- 0.5*antelope_abate_drought*tau_star_drought
antelope_post_trade_cost_d
ventura_post_trade_cost_d <- 0.5*ventura_abate_drought*tau_star_drought
ventura_post_trade_cost_d

#Take into account cost of AF sold or bought based on the difference in abatement before and after trading
kern_trade_money_d <- (kern_trade_abatement_d-59.7)*(tau_star_drought)
kern_trade_money_d
#Kern abated more than with the 1/3, so subtract amount made from selling from total cost
kern_trade_cost_d <- kern_post_trade_cost_d-kern_trade_money_d
kern_trade_cost_d

mojave_trade_money_d <- (mojave_trade_abatement_d - 84.28)*(tau_star_drought)
mojave_trade_money_d
#Mojave abated less than with the 1/3, so add amount spent from buying extra to total cost 
mojave_trade_cost_d <- mojave_post_trade_cost_d-mojave_trade_money_d
mojave_trade_cost_d

antelope_trade_money_d <- (antelope_trade_abatement_d - 132.44)*tau_star_drought
antelope_trade_money_d
#Antelope abated less than with the 1/3, so add amount spent from buying extra to total cost
antelope_trade_cost_d <- antelope_post_trade_cost_d-antelope_trade_money_d
antelope_trade_cost_d

ventura_trade_money_d <- (ventura_trade_abatement_d - 147.49)*tau_star_drought
ventura_trade_money_d
#Ventura abated more than with the 1/3, so subtract amount made from selling from total cost
ventura_trade_cost_d <- ventura_post_trade_cost_d - ventura_trade_money_d
ventura_trade_cost_d
```


