---
title: "204_hw2"
author: "Katherine Rosencrance"
date: "4/21/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# attach packages
library(here)
library(tidyverse)

```

# #1. Plot marginal abatement cost data for each irrigation district
```{r}
#Read in the data
water_districts <- read_csv(here("Water_Districts.csv"))

# plot data from each district
district_plot <- ggplot(data = water_districts, aes(x= Reduction)) + 
  geom_smooth(method = "lm", aes(y = MC_Kern), color = "darkred") + 
  geom_smooth(method = "lm", aes(y = MC_Mojave), color="steelblue")+
  geom_smooth(method = "lm", aes(y = MC_Antelope), color = "green")+
  geom_smooth(method = "lm", aes(y = MC_Ventura), color = "yellow")+
  labs(x = "Reduction in AF", y = "Price ($/AF) ")+
  theme_classic()
district_plot

```

```{r}
# plot data for each district separately
MC_kern <- ggplot(data = water_districts, aes(x = Reduction, y = MC_Kern))+
  geom_point()
MC_kern

MC_mojave <- ggplot(data = water_districts, aes(x = Reduction, y = MC_Mojave))+
  geom_point()
MC_mojave

MC_antelope <- ggplot(data = water_districts, aes(x = Reduction, y = MC_Antelope))+
  geom_point()
MC_antelope

MC_ventura <- ggplot(data = water_districts, aes(x = Reduction, y = MC_Ventura))+
  geom_point()
MC_ventura
```

```{r}
# linear models for each district
model_kern <- lm(MC_Kern ~ 0 + Reduction, data= water_districts)
B = model_kern$coefficient[1]
predicted_mc_kern <- B*seq(0, 150, 500)

model_mojave <- lm(MC_Mojave ~ 0 + Reduction, data= water_districts)
B = model_mojave$coefficient[1]
predicted_mc_mojave <- B*seq(0, 150, 500)

model_antelope <- lm(MC_Antelope ~ 0 + Reduction, data= water_districts)
B = model_antelope$coefficient[1]
predicted_mc_antelope <- B*seq(0, 150, 500)

model_ventura <- lm(MC_Ventura ~ 0 + Reduction, data= water_districts)
B = model_ventura$coefficient[1]
predicted_mc_ventura <- B*seq(0, 150, 500)

summary(model_kern)
summary(model_antelope)
summary(model_mojave)
summary(model_ventura)

# store slopes
kern_slope <- model_kern$coefficient[1]
mojave_slope <- model_mojave$coefficient[1]
antelope_slope <- model_antelope$coefficient[1]
ventura_slope <- model_ventura$coefficient[1]
```

# #2.Derive each districts demand curve for water

```{r}
#Baselines
kern_baseline <- 150
mojave_baseline <- 140 
antelope_baseline <- 220
ventura_baseline <- 245

# Demand/use equations stored as functions
kern_mb <- function(x){kern_slope*(kern_baseline-x)}
mojave_mb <- function(x){mojave_slope*(mojave_baseline-x)}
antelope_mb <- function(x){antelope_slope*(antelope_baseline-x)}
ventura_mb <- function(x){ventura_slope*(ventura_baseline-x)}

# Plot demand curves
ggplot(data.frame(x = c(0,250)), aes(x = x)) +
  stat_function(fun = kern_mb, color = "darkred")+
  stat_function(fun = mojave_mb, color = "steelblue")+
  stat_function(fun = antelope_mb, color = "green")+
  stat_function(fun = ventura_mb, color = "yellow")+
  theme_minimal()+
  ylim(0, 750) +
  labs(x = "Water used (AF)", y = "Price ($/AF)", title = "Demand for Water")
```
# #3 (1) calculate the stringency of the policy (defined below for each intervention) required to achieve the 500 AF target, (2) calculate the total cost of meeting the target using that approach, (3) calculate the cost to each district, and (4) calculate the tax revenue generated

## Cap without trade
```{r}
# stringency of policy = 255/755 or 0.338

# Total cost of meeting target

# P* using the new Q* based on abatement
kern_p <- {kern_slope*(kern_baseline-99.3)}
mojave_p <- {mojave_slope*(mojave_baseline-92.68)}
antelope_p <- {antelope_slope*(antelope_baseline-145.64)}
ventura_p <- {ventura_slope*(ventura_baseline-162.19)}

kern_p
mojave_p
antelope_p
ventura_p

# calculate area of triangle using 1/2(P*)(change in Q) to get individual costs
kern_cost <- 0.5*(kern_p)*(50.7)
mojave_cost <- 0.5*(mojave_p)*(47.32)
antelope_cost <- 0.5*(antelope_p)*(74.36)
ventura_cost <- 0.5*(ventura_p)*(82.81)

# total cost by adding up all district costs
total_cost <- kern_cost +
mojave_cost +
antelope_cost +
ventura_cost

total_cost

```

## Tax on water use
```{r}
# stringency calculated by horizontally summing the 4 MC(A) curves
horizontal_sum <- (1/kern_slope)+(1/mojave_slope)+(1/antelope_slope)+(1/ventura_slope)
tau_star <- 255/horizontal_sum
tau_star

#calculate total cost by getting area of triangle from aggregate MC curve
total_cost <- 0.5*tau_star*255
total_cost

#calculate individual cost for each district

#determine abatement for each district
kern_abate <- (1/kern_slope)*tau_star
mojave_abate <- (1/mojave_slope)*tau_star
antelope_abate <- (1/antelope_slope)*tau_star
ventura_abate <- (1/ventura_slope)*tau_star

kern_abate
mojave_abate
antelope_abate
ventura_abate

#determine area of triangle using abatement and tax (tau_star)
kern_cost_tax <- 0.5*(kern_abate*tau_star)
mojave_cost_tax <- 0.5*(mojave_abate*tau_star)
antelope_cost_tax <- 0.5*(antelope_abate*tau_star)
ventura_cost_tax <- 0.5*(ventura_abate*tau_star)

kern_cost_tax
mojave_cost_tax
antelope_cost_tax
ventura_cost_tax

# determine tax revenue by multiplying tax by abatement
government_revenue <- tau_star*255
government_revenue

```
## Cap and trade
```{r}
# calculate stringency of policy

# total cost of meeting approach

# total cost to each district


```

